A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-05-16 manuscript.Rmd
clarified section on singularity vs docker

This flexibility to fully control the software environment is of particular interest for software infrastructures where the user cannot install software themself, because of limited rights e.g. on cloud computing platforms or High-Performance Computing Clusters. However, executing docker itself needs special rights which are seldomly granted on High-Performance Computing Cluster. For this case, Singularity provides a fully compatible alternative (see Section under [Linux]).

>>>>

The flexibility to fully control the software environment is of particular interest for software infrastructures where users cannot install software because of limited access rights, for example, on cloud computing platforms or high-performance computing clusters. However, running docker needs unrestricted access rights to the system, which are rarely granted on those platforms. For this case, Singularity provides a fully compatible alternative (see Section under [Linux]) that can be executed with limited access rights.
